Accelerated Inference for Partially Observed Stochastic Processes with Automatic Differentiation

### 2023-12-28 mop/draft.tex
Updates from Overleaf

\begin{figure}
    \centering
    \includegraphics{imgs/095/qq.png}
    \caption{Caption}
    \label{fig:enter-label}
\end{figure}

>>>>

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.53]{imgs/095/pairs.png}
    \includegraphics[scale=0.53]{imgs/095/qq.png}
    \caption{Scatterplots depicting the performance of IFAD against that of IF2. Left: Paired searches from the same starting point. Right: Q-Q plot of ranked IFAD searches against ranked IF2 searches. It is clear that on average, IFAD has the edge, and manages to find the MLE while no IF2 search successfully gets within 5 log-likelihood units of it. }
    \label{fig:scatter}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics{imgs/095/boxplot.png}
    \caption{Caption}
    \label{fig:enter-label}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics{imgs/095/optim.png}
    \caption{Caption}
    \label{fig:enter-label}
\end{figure}

\begin{figure}[u]
    \centering
    \includegraphics{imgs/095/hist.png}
    \caption{Caption}
    \label{fig:enter-label}
\end{figure}
